Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-12 manuscript/manuscript.tex
Density-based discretization figure changed to only one line
Added density-based discretization figure explanation on manuscript

@@

Lets assume an arbitrary tesseroid with boundary radii $R_1$ and $R_2$ 
and a density function $\rho(r')$ which we will call the 
\emph{original tesseroid}, whose radial dimension can be written as
$L_r = R_2 - R_1$.

@@

\noindent Because this algorithm will be iteratively applied for every 
subdividing tesseroid, we'd like to note that this normalised density 
function will be the same for every subdividing tesseroid.
In case that the density function is constant, both the maximum and 
minimum densities are equal and the normalised function could not 
be defined, so the density-based discretization algorithm won't be 
applied.

@@

It's easy to see that the delta ratio indirectly controls how many 
times the tesseroids will be subdivided based on the variation of the 
density function.

Therefore it determines the accuracy involving the numerical error that 
the density variation introduces and also the computation time.
This raises the need to determine a maximum value of $\delta$ that 
ensures an acceptable accuracy while minimising the computation time. 
We will perform this determination with the same methodology as the one 
applied to the $D$ ratio: compare the numerical model with the 
analytical solutions for a spherical shell.

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example intended to show how the density-based algorithm works.}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

Lets assume an arbitrary \emph{original} tesseroid with boundary radii 
$R_1$ and $R_2$ and a density function $\rho(r')$, whose radial 
dimension can be written as $L_r = R_2 - R_1$.

@@

Because the algorithm will be iteratively applied for every 
subdividing tesseroid, we'd like to note that this normalised density 
function will be the same for every subdividing tesseroid.
In case that the density function is constant, both the maximum and 
minimum densities are equal and the normalised function could not 
be defined, so the density-based discretization algorithm won't be 
applied.

@@

On Figure \ref{fig:density-discretization-algorithm}(a) we propose an 
arbitrary normalised density function as an example of how this 
algorithm works.
And we plotted its corresponding linear function $\rho_l(r')$ and a 
dashed line that represents the maximum absolute difference $\Delta 
\rho (r')$.
We will assume that the discretization inequation 
\ref{eq:delta-density} holds in this case, so we must divide the 
tesseroid at the height at which the maximum difference occurs.
The dots on Figure \ref{fig:density-discretization-algorithm} 
represent the discretization heights, i.e. the radial boundaries of the 
subdiving tesseroids produced by the algorithm.

On Figure \ref{fig:density-discretization-algorithm}(b) we apply the 
algorithm on the shallower subdividing tesseroid.
In the same way, we propose the linear function and compute the maximum 
absolute difference $\Delta \rho (r')$.
In this case, the tesseroid size-ratio $L_r^\text{sm}/L_r$ is lower 
than one and will be taken into account in the discretization 
inequation, which will be assumed to hold also in this case, leading to 
the division of this tesseroid.

On Figure \ref{fig:density-discretization-algorithm}(c) we perform the 
same analysis on the deeper subdiving tesseroid, and assuming that the 
inequality holds in this case we also subdivide it.

Finally, if we suppose that the value of $\delta$ used in this example 
does not produce further discretizations, the resulting subdiving 
tesseroids can be seen on Figure 
\ref{fig:density-discretization-algorithm}(d).

It's easy to see that the delta ratio indirectly controls how many 
times the tesseroids will be subdivided based on the variation of the 
density function.
Therefore it determines the accuracy involving the numerical error that 
the density variation introduces and also the computation time.
This raises the need to determine a maximum value of $\delta$ that 
ensures an acceptable accuracy while minimising the computation time. 
We will perform this determination with the same methodology as the one 
applied to the $D$ ratio: compare the numerical model with the 
analytical solutions for a spherical shell.
